---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# plottie

<!-- badges: start -->
<!-- badges: end -->

The `plottie` package provides a simple set of functions for quickly creating basic ggplot2 visualizations without writing full ggplot code manually.

## Installation

You can install the development version of plottie from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("aylahauser/plottie")
```

## Usage

Given two numeric variables, the `easy_scatterplot()` function creates a scatterplot in the plot window using ggplot2.
Users can customize point color and pass additional ggplot2 arguments such as size, alpha, etc.

```{r}
library(plottie)

mtcars$cyl <- as.factor(mtcars$cyl)
mtcars$gear <- as.factor(mtcars$gear)

easy_scatterplot(mtcars, x = "wt", y = "mpg", color = "cyl")
```

Given a categorical variable, the `easy_barplot()` function creates a barplot in the plot window using ggplot2.
Users can customize the fill color and pass additional arguments like width, alpha, etc.

```{r}
easy_barplot(mtcars, x = "cyl", fill = "gear")
```

Given a numeric variable, the `easy_histogram()` function creates a histogram in the plot window using ggplot2.
Users can customize fill color and provide extra arguments such as bins, alpha, etc.

```{r}
easy_histogram(mtcars, x = "mpg", fill = "cyl")
```

Given one categorical and one numeric variable, the `easy_boxplot()` function creates a boxplot in the plot window using ggplot2.
Users can customize a color and add extra ggplot2 arguments like width, alpha, etc.

```{r}
easy_boxplot(mtcars, x = "cyl", y = "mpg", color = "blue")
```

Given two numeric variables, the `easy_lineplot()` function creates a line plot in the plot window using ggplot2.
Users can customize the line color and pass additional arguments such as size, linetype, etc.

```{r}
easy_lineplot(mtcars, x = "hp", y = "mpg", color = "red")
```

Given one or two variable names, the `plot_helper()` function suggests an appropriate plot type based on variable types.
It returns a short message indicating the plot type that is recommended.

```{r}
library(ggplot2)

plot_helper(mpg, x = "cty", y = "hwy")
```

