---
title: "Using the plottie package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the plottie package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(plottie)
```

## Easy Plotting with plottie

The main function of the plottie package is to make plotting using ggplot2 in R simpler and more accessible. Let's see how we can accomplish this. First, load the `plottie` package.

Then, use the `plot_helper` function to help you decide what plot to build based on your data set and the variables you want to use within it. We will be using the built in package dataset called `students` which holds identification variables about hypothetical students in an elementary school classroom. Let's say we want to analyze the relationship between the gender of the student and their age.  

```{r}
plot_helper(data = students, x = "female_logical", y = "age_numerical")
```

Now, that the plot helper has determined what types of graphs we can use to plot our data most effectively, lets choose one of the coordinating graph functions built into the `plottie` package. We will be using the `easy_boxplot()` function, but `easy_barplot()` would work for this type of data as well. The `easy_boxplot()` function will take our the arguments used in the `plot_helper` function and an additional variable to color the plot by.

```{r}
easy_boxplot(data = students, x = "female_logical", y = "age_numerical", color = "favorite_class_categorical")
```

## Plottie Data
As aforementioned, the `plottie` package also come with a built-in data set that includes attributes about 11 students in a hypothetic elementary school class. This data set comes with logical, numeric, and categorical variables to give examples of how to make easy plots from multiple variable types.

```{r}
plottie::students
```




